Carbonate chemistry at Ny-Ålesund

### 2022-12-26 awipev-CO2.Rmd
Cleanup after fixing durafet calculation issue

```{r durafet calibration, echo=FALSE, message= FALSE, warning=FALSE}
# deployment period between 2 spectro measurements.
# TODO the following throws a warning but seems to work
durPeriod <- d_all %>%
  dplyr::select(datetime, ph_s_dur_temp_fb) %>%
  dplyr::filter(!is.na(ph_s_dur_temp_fb))
durPeriod <- durPeriod %>% 
  #dplyr::arrange(datetime) %>%
  dplyr::mutate(middle =  
                  seconds_to_period(c(0, difftime(time1 = datetime[-1], 
                                                  time2 = datetime[-nrow(durPeriod)])/2* 3600 ))) %>%
  dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])

>>>>

```{r durafet calibration, echo=FALSE, message= FALSE, warning=FALSE}
# deployment period between 2 spectro measurements.
# the following thrown an error fixed 2022-12-26
durPeriod <- d_all %>%
  dplyr::select(datetime, ph_s_dur_temp_fb) %>%
  dplyr::filter(!is.na(ph_s_dur_temp_fb))
durPeriod <- durPeriod %>% 
  #dplyr::arrange(datetime) %>%
  dplyr::mutate(middle =  
                  seconds_to_period(c(0, difftime(time1 = datetime[-1], 
                                                  time2 = datetime[-nrow(durPeriod)])/2* 3600 ))) %>%
  #dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])
  dplyr::mutate(dur_interval = datetime + middle)
